Trending assessment for nowcasts, measurements, and forecasts

### 2024-02-22 paper.tex
Update 18.2.2024
Update bootstrapping
Improve manuscript
Update on Overleaf.

%%% --- Tabulars
\usepackage{booktabs}
\usepackage{multirow} % cells over several rows
\usepackage{tabularx}
%\usepackage{tabularray}

@@

\usepackage{xargs,ifthen} % Use optional arguements in commands
\newcommandx{\unsure}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
\newcommandx{\missing}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
\newcommandx{\change}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
\newcommandx{\info}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}}
\newcommandx{\improvement}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}}
\newcommandx{\thiswillnotshow}[2][1=]{\todo[disable,#1]{#2}}
\usepackage{marginnote}
\let\marginpar\marginnote

%%% --- Acronyms
\usepackage{acro}
\DeclareAcronym{kde}{short=KDE, long=kernel density estimation}
\DeclareAcronym{bca}{short=BCa, long=bias-corrected and accelerated}

@@

%%% --- ToDo List
\usepackage{enumitem}
\newlist{todolist}{itemize}{2}
\setlist[todolist]{label=$\square$}
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\newcommand{\done}{\rlap{$\square$}{\raisebox{2pt}{\large\hspace{1pt}\cmark}}%
\hspace{-2.5pt}}
\newcommand{\wontfix}{\rlap{$\square$}{\large\hspace{1pt}\xmark}}

@@

Agenda für heute:
\begin{itemize}
    \item Aufteilung
    \begin{itemize}
        \item Introduction (1.5 pages), Conclusion (0.5 pages), Abstract
        \item Nowcasting (1 pages): Bolin
        \item Trending (5-6 pages): Jonas fängt an
        \item Application (5-6 pages): Jonas
    \end{itemize}
    \item Datenquellen
\end{itemize}

\begin{itemize}    
    \item Journal/Anwendungsgebiet klären: Angewandtes Medizin Statistikjournal? Dann müsste man die folgenden Abschnitte entsprechend ausrichten
\end{itemize}

@@

\appendix
\section{Data generation for Section~\ref{sec:trending}}\label{sec:app-trending-data-generation}

\todo{Write}

Beispiel
\begin{itemize}
  \item $\diffyt \sim U(-5, 5) + N(0, 1)$
  \item $\diffxt \sim \diffyt \cdot \SBer(k) \cdot (\text{Truncated Normal, mean 1, sigma 0.5, trunc 0})$
\end{itemize}

>>>>

%%% --- Tabulars
\usepackage{booktabs}
\usepackage{multirow} % cells over several rows
\usepackage{tabularx}
%\usepackage{tabularray}
\usepackage{etoolbox}
\AtBeginEnvironment{tabular}{\small}

@@

\usepackage{xargs,ifthen} % Use optional arguements in commands
\newcommandx{\unsure}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
\newcommandx{\discuss}[2][1=]{\todo[linecolor=orange,backgroundcolor=orange!25,bordercolor=orange,#1]{#2}}
\newcommandx{\missing}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
\newcommandx{\change}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
\newcommandx{\info}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}}
\newcommandx{\improvement}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}}
\newcommandx{\done}[2][1=]{\todo[linecolor=gray,backgroundcolor=gray!25,bordercolor=gray,#1]{#2}}
\newcommandx{\thiswillnotshow}[2][1=]{\todo[disable,#1]{#2}}
\usepackage{marginnote}
\let\marginpar\marginnote

%%% --- Acronyms
\usepackage{acro}
\DeclareAcronym{kde}{short=KDE, long=kernel density estimation}
\DeclareAcronym{bca}{short=BCa, long=bias-corrected and accelerated}
\DeclareAcronym{cdf}{short=CDF, long=cumulative distribution function}

@@

%%% --- ToDo List
%\usepackage{enumitem}
%\newlist{todolist}{itemize}{2}
%\setlist[todolist]{label=$\square$}
%\usepackage{pifont}
%\newcommand{\cmark}{\ding{51}}%
%\newcommand{\xmark}{\ding{55}}%
%\newcommand{\done}{\rlap{$\square$}{\raisebox{2pt}{\large\hspace{1pt}\cmark}}%
%\hspace{-2.5pt}}
%\newcommand{\wontfix}{\rlap{$\square$}{\large\hspace{1pt}\xmark}}

@@

\begin{itemize}
    \item Aufteilung
    \begin{itemize}
        \item Introduction (1.5 pages): Bolin fängt an, Conclusion (0.5 pages), Abstract
        \item Application areas (1 pages): Bolin
        \item Trending (5-6 pages): Jonas fängt an
        \item Application (5-6 pages): Jonas
    \end{itemize}
    \item Datenquellen
\end{itemize}

\begin{itemize}    
    \item Journal/Anwendungsgebiet klären: Angewandtes Medizin Statistikjournal: z.B. BMC Medical Research Methodology
\end{itemize}

@@

\appendix
\section{Data generation for Section~\ref{sec:trending}}\label{sec:app-trending-data-generation}
\input{sections/50-appendix-data-generation}

### 2024-02-22 sections/01-introduction.tex
Update on Overleaf.

>>>>

The paper is organized as follows. In Section \ref{sec:notation}, we compare the three possible application areas for trending assessment: measurement, forecasting and nowcasting, and define the time series of change according to the application for a given time series. In Section \ref{sec:trending}, we formalise the concept of trending independently of the application domain and investigate quantification approaches. In particular, we introduce a new graphical method for evaluating trending, the conditional trending plot, which can represent the simultaneous evaluation of different intervals and asymmetries. Bootstrap methods for calculating confidence intervals for trending measures are also presented. In Section \ref{sec:application}, we show the results of applying our method to several practical examples from measurement, forecasting and nowcasting. We conclude our paper with the last section.
